Modeling the near-wake of a vertical-axis cross-flow turbine with 2-D and 3-D RANS

### 2015-09-14 paper.tex
A comma

Despite the development of many simple engineering models based on blade element
momentum or vortex modeling, it remains difficult to predict the performance of
cross-flow turbines in all cases---namely when solidity or blade chord to radius
ratio is high---a common characteristic of the smaller CFTs. With computing
power becoming evermore available and affordable, computational fluid dynamics
(CFD) presents an attractive method for simulating cross-flow turbines since it
only requires turbulence modeling, i.e., the machine is described from first
principles. However, CFD can be computationally expensive when done in three
dimensions, which may be necessary in some cases. There are many examples in the
literature of 2-D cross-flow turbine simulations with widely varying results.
Balduzzi et al. provides a summary of recent computations and an attempt to
standardize a methodology for using Reynolds-averaged Navier--Stokes (RANS) to
correctly simulate performance of a 2-D CFT \cite{Balduzzi2016}.

>>>>

Despite the development of many simple engineering models based on blade element
momentum or vortex modeling, it remains difficult to predict the performance of
cross-flow turbines in all cases---namely when solidity, or blade chord to
radius ratio is high---a common characteristic of the smaller CFTs. With
computing power becoming evermore available and affordable, computational fluid
dynamics (CFD) presents an attractive method for simulating cross-flow turbines
since it only requires turbulence modeling, i.e., the machine is described from
first principles. However, CFD can be computationally expensive when done in
three dimensions, which may be necessary in some cases. There are many examples
in the literature of 2-D cross-flow turbine simulations with widely varying
results. Balduzzi et al. provides a summary of recent computations and an
attempt to standardize a methodology for using Reynolds-averaged Navier--Stokes
(RANS) to correctly simulate performance of a 2-D CFT \cite{Balduzzi2016}.
